Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-11 docs/google-research-awards-latam/main.tex
another pass on proposal

% \usepackage{natbib}
% \setlength{\bibsep}{0pt plus 0.3ex}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.3\baselineskip}
%,nohead,nofoot
%\usepackage[margin=1n,left=1cm,top=1cm,right=1.75cm,bottom=1.5cm]{geometry}
\usepackage[margin=1in,includeheadfoot,left=1cm,top=0.5cm,right=1.5cm,bottom=0.5cm]{geometry}
%\usepackage[margin=1in,includeheadfoot]{geometry}
\usepackage{url}
\usepackage{cite}
\usepackage{lipsum}
\usepackage{booktabs}
\usepackage{tabularx}

@@

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify}. Its niche is front-end and
back-end web development\Comment{, supported several frameworks and
  runtimes (\eg{}, Express.js and Node.js)}.

Engine implementations (\eg{}, Google's V8\Fix{cite}, Mozilla's
SpiderMonkey\Fix{cite}, and Microsoft's Chakra\Fix{cite}) need to
follow the constant changes in the language
specification~\cite{kangax}. Recently, the JavaScript
specification went through a bigger change compared to prior
releases\footnote{Called by the name of ECMAScript6
  (ES6)~\cite{es6-features}}. As in any piece of software, changes in
the specification often demand sensible changes in implementations
that could lead to errors, including regressions. In fact, bugs in JS
implementations are often reported by the general public, some of
which were reported by our team.

%% (confirmed by engine developers; see
%% Section~\ref{sec:results}) using a prototype of our solution (see
%% Section~\ref{sec:design}).

The lack of executable specifications that could be used as oracles is
an important obstacle for test generation--it prevents detection of
errors which are not explicit, like a crash.  The novelty of our
approach is the use of multiple engine implementations to assess input
validity and output correctness. \emph{Differential testing}\Fix{cite}
has been applied in a variety of contexts\Fix{cite cite}, but it has
not been used to find functional bugs in JS engines.

%\vspace{-1ex}
\begin{center}
\fbox{
  \begin{minipage}{11.75cm}
    \centering \textit{The goal of this project is to find bugs in
      implementations of JavaScript engines by leveraging diversity
      across implementations.}
  \end{minipage}
}
\end{center}
%\vspace{-1ex}

@@

Fuzzing is a popular technique to generate new test inputs from
existing inputs\Fix{cite} with the typical goal of finding
crashes. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are generated (\eg{},
mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
random-based\Fix{cite}) and whether or not coverage information is
taken into account in the fuzzing process.

\begin{figure}[htbp]
  \centering
  \includegraphics[trim=0 350 200 0,clip,width=0.5\textwidth]{google-awards-workflow}
  \label{fig:workflow}
  \caption{Workflow of Infrastructure.}
\end{figure}

@@

\vspace{1ex}\noindent\textbf{Input/Output.}~...

>>>>

% \usepackage{natbib}
% \setlength{\bibsep}{0pt plus 0.3ex}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.3\baselineskip}
%,nohead,nofoot
%\usepackage[margin=1n,left=1cm,top=1cm,right=1.75cm,bottom=1.5cm]{geometry}
\usepackage[margin=1in,includeheadfoot,left=1cm,top=0.5cm,right=1.5cm,bottom=0.5cm]{geometry}
%\usepackage[margin=1in,includeheadfoot]{geometry}
\usepackage{url}
\usepackage{cite}
\usepackage{lipsum}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{wrapfig}

@@

%% Its niche is front-end and
%% back-end web development\Comment{, supported several frameworks and
%%   runtimes (\eg{}, Express.js and Node.js)}.

%% In fact, bugs in JS implementations are often reported by
%% the general public, some of which were reported by our team.
%% (confirmed by engine developers; see
%% Section~\ref{sec:results}) using a prototype of our solution (see
%% Section~\ref{sec:design}).

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify} largely because of its
widespread use on the web. As common in software, the JS specification
changes regularly\footnote{Recently, the specification went through a
  bigger change compared to prior releases, called by the name of
  ECMAScript6 (ES6)~\cite{es6-features}} to accomodate pressing
demands~\cite{kangax} and these changes often entail sensible changes
in engine implementations that could lead to errors, including
regressions.  Test generation can help reduce the cost of testing, but
the lack of executable specifications is an important obstacle for
finding functional errors.

%\vspace{-1ex}
\begin{center}
\fbox{
  \begin{minipage}{13.5cm}
    \centering \textit{The goal of this project is to find bugs in
      implementations of JavaScript engines by leveraging diversity
      across implementations.}
  \end{minipage}
}
\end{center}
%\vspace{-1ex}

The novelty of our proposal is the use of multiple engine
implementations (\eg{}, Google's V8, Microsoft's Chakra, etc.) to
assess input validity and to check output
correctness. \emph{Differential testing}\Fix{cite} has been applied in
a variety of contexts\Fix{cite cite}, but it has not been used to find
functional bugs in JS engines.

@@

\begin{wrapfigure}[13]{r}[0pt]{0.45\textwidth}
\vspace{-5ex}
%\begin{figure}[htbp]
  \centering
  \includegraphics[trim=0 350 200 0,clip,width=0.5\textwidth]{google-awards-workflow}
  \label{fig:workflow}
  \caption{Workflow of Infrastructure.}
%\end{figure}
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs\Fix{cite} with the typical goal of finding
crashes. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are generated (\eg{},
mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
random-based\Fix{cite}) and whether or not coverage information is
taken into account in the fuzzing process. Figure~\ref{fig:workflow}
shows a generic pipeline of a fuzzer. JS files are provided as seeded
inputs to bootstrap the process. These files can originate from the
test suites of the engine codebases or from the bug reports in their
issue trackers. \Fix{elaborate}

@@
